PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-06-15 paper/ms.tex
minor

\explain{Note: added citation to Bodman et al 2017 in this paragraph.}
These light curves have been phenomenologically classified as
``persistent flux dips'' or ``transient flux dips'', based on whether
their depths and durations show variability over the 90-day K2
campaigns \citep{stauffer_orbiting_2017}.  In the terminology of
\citet{stauffer_orbiting_2017}, these objects are morphologically
distinct from ``scallop shell'' light curves, and are present in stars
at more advanced evolutionary disk stages than the ``dipper'' stars
\citep{ansdell_young_2016,bodman_dippers_2017,cody_manyfaceted_2018}.
The persistent and transient flux dip stars all show angular dips that
are cannot be explained as the effects of starspots.  These stars
typically have the following things in common:
\begin{enumerate}[topsep=0.5ex,itemsep=-0.5ex,partopsep=1ex,parsep=1.5ex]
  \item They are weak-lined T Tauri stars.
  \item The spectral type is M2 to M5 ({\it e.g.},
    \citealt{rebull_usco_2018},~Figure~20).
  \item \replaced{The age is typically $\lesssim$ 100$\,$Myr.}{The
    ages typically range between 5 and 100$\,$Myr.}\footnote{ At
    present, the oldest observed ``scallops'' are in the Pleaides
    \citep{rebull_rotation_2016}. One of these, EPIC 211013604, might
    meet the ``persistent dip'' classification.  If so, it is \deleted{also} the
    oldest known. \added{The lower limit comes from the lack of detectable
   WISE infrared excesses.}} 
  \item The light curves show shallow, angular dips, \deleted{usually}
    superposed on large-amplitude smooth variability \added{at or near
    1:1 synchronicity}. The \replaced{latter}{smooth variability} is
    interpreted as stellar rotation.
  \item The rotation is rapid, with a period that is usually between
    0.5 and 2.0 days.
  \item There is rarely any infrared excess that is detectable in the
    WISE data (never any W4 detection; only a few W3 detections).
  \item They sometimes show multiple dips per cycle.
  \item The dip depths, durations, and phases can vary over just a few
    cycles ({\it e.g.}, EPIC 204143627).
  \item The dip depths can change after flares.
  \item They are rare at a population level, with an occurrence rate
  \replaced{of $\lesssim 1\%$}{between 0.1--1\%}
   of young M2-M5 stars \citep{rebull_usco_2018}.
\end{enumerate}
The 10.76$\,$hr signal in \ptfo\ meets all of these criteria.  This is
the first connection of \ptfo\ with this class of objects, likely
because the TESS data enabled us to put the dips in the context of the
asymmetric out-of-dip modulation.

>>>>

\explain{Note: added citation to Bodman et al 2017 in this paragraph.}
These light curves have been phenomenologically classified as
``persistent flux dips'' or ``transient flux dips'', based on whether
their depths and durations show variability over the 90-day K2
campaigns \citep{stauffer_orbiting_2017}.  In the terminology of
\citet{stauffer_orbiting_2017}, these objects are morphologically
distinct from ``scallop shell'' light curves, and are present in stars
at more advanced evolutionary disk stages than the ``dipper'' stars
\citep{ansdell_young_2016,bodman_dippers_2017,cody_manyfaceted_2018}.
The persistent and transient flux dip stars all show angular dips that
are cannot be explained as the effects of starspots.  These stars
typically have the following things in common:
\begin{enumerate}[topsep=0.5ex,itemsep=-0.5ex,partopsep=1ex,parsep=1.5ex]
  \item They are weak-lined T Tauri stars.
  \item The spectral type is M2 to M5 ({\it e.g.},
    \citealt{rebull_usco_2018},~Figure~20).
  \item \replaced{The age is typically $\lesssim$ 100$\,$Myr.}{The
    ages typically range between 5 and 100$\,$Myr.}\footnote{ At
    present, the oldest observed ``scallops'' are in the Pleaides
    \citep{rebull_rotation_2016}. One of these, EPIC 211013604, might
    meet the ``persistent dip'' classification.  If so, it is \deleted{also} the
    oldest known. \added{The lower limit comes from the lack of detectable
   WISE infrared excesses.}} 
  \item The light curves show shallow, angular dips, \deleted{usually}
    superposed on large-amplitude smooth variability \added{at or near
    1:1 synchronicity}. The \replaced{latter}{smooth variability} is
    interpreted as stellar rotation.
  \item The rotation is rapid, with a period that is usually between
    0.5 and 2.0 days.
  \item There is rarely any infrared excess that is detectable in the
    WISE data (never any W4 detection; only a few W3 detections).
  \item They sometimes show multiple dips per cycle.
  \item The dip depths, durations, and phases can vary over just a few
    cycles ({\it e.g.}, EPIC 204143627).
  \item The dip depths can change after flares.
  \item They are rare at a population level, with an occurrence rate
  \replaced{of $\lesssim 1\%$}{between 0.1--1\%}
   of young M2-M5 stars \citep{rebull_usco_2018}.
\end{enumerate}
The 10.76$\,$hr signal in \ptfo\ meets all of these criteria.
\replaced{This is the first connection of \ptfo\ with this class of
objects, likely because the TESS data enabled us to put the dips in
the context of the asymmetric out-of-dip modulation.} {While this was
in fact already noted by \citet{stauffer_orbiting_2017}, the
asymmetric out-of-dip modulation shown by the TESS data puts the
connection on stronger footing.}
